Tight Generalization Bounds for Hard Parameter Sharing in High-dimensional Linear Regression

### 2020-10-17 arxiv/proof_examples.tex
appendix

h(x):= [(1-x^{-1})^2\kappa^2 + (1+x^{-2})d^2/2] \cdot p^{-1} \tr\left[\left([(X^{(2)})^\top X^{(2)}]^{-1} + x^{-2} [(X^{(1)})^\top X^{(1)}]^{-1}\right)^{-1}\right].

@@

h'(x) \ge \left[2(1-x^{-1})\frac{\kappa^2}{x^2} - \frac{d^2}{x^3}\right] \cdot p^{-1} \tr\left[\left([(X^{(2)})^\top X^{(2)}]^{-1} + x^{-2} [(X^{(1)})^\top X^{(1)}]^{-1}\right)^{-1}\right] \ge 0,

@@

as long as $x \ge 1+d^2/(2\kappa^2)$.

@@

	h'(x)\le [-2(1-x)\kappa^2 + xd^2] \cdot p^{-1} \tr\left[\left(x^2[(X^{(2)})^\top X^{(2)}]^{-1} + [(X^{(1)})^\top X^{(1)}]^{-1}\right)^{-1}\right]\le 0,

@@

as long as $x\le 1-d^2/(2\kappa^2)$. In sum, we see that the minimizer $x^\star$ must satisfy
$$1-d^2/(2\kappa^2)\le x^\star \le 1+d^2/(2\kappa^2).$$

@@

Now we are ready to prove equation \eqref{hatw_add1}. First, using equations \eqref{op_uplow} and  \eqref{h'(A)1}, we obtain that for $1+d^2/\kappa^2 \le x\le 1+\delta$,
$$h'(x)\ge \frac{2(x-1)\kappa^2 - d^2}{x^3} \cdot p^{-1} \tr\left[\left([(X^{(2)})^\top X^{(2)}]^{-1} + x^{-2} [(X^{(1)})^\top X^{(1)}]^{-1}\right)^{-1}\right] \gtrsim p\left(d^2 + |x-1|\kappa^2\right).$$
Thus we get that if $1+2d^2/\kappa^2 +p^{-1/4+c}\le x\le 1+\delta$,
\begin{align*}
h(x)-h(1)\ge h(x)-h(1+d^2/\kappa^2) \ge \int_{1+d^2/\kappa^2}^x h'(x)\dd x \gtrsim p\kappa^2 \cdot |x-1|^2  \gtrsim p\frac{d^4}{\kappa^2} + p^{-1/2+2c}\cdot p\kappa^2 .
\end{align*}
On the other hand, by Claim \ref{claim_largedev1} we have that
$$ g(x)=h(x)+\sigma^2 (n_1+n_2-p)+\OO \left(p^{1/2+c}\left(\sigma^2 +\kappa^2+d^2 \right)\right)$$
with high probability. Combining the above two estimates, we obtain that under the conditions $\sigma^2 \lesssim  \kappa^2$ and $d^2 \le p^{-c_{\varphi}}{\kappa^2}$,
$$g(x)-g(1) = h(x)-h(1) + \OO \left(p^{1/2+c}\left(\sigma^2 +\kappa^2+d^2 \right)\right) >0$$
with high probability, i.e. $x$ cannot be the minimizer of $g$.
%Then if we choose the constant $c$ in Claim \ref{claim_largedev1} such that $e_1<2e_2$, we have
%$$ h(x)-h(1)\gtrsim  p^{-1/2+2e_2}\cdot p\kappa^2 \gg p^{-1/2+e_1}\cdot p\left(\sigma^2 +\kappa^2+d^2 \right),$$ where we use the assumption that $\sigma^2$ and $d^2$ are both at most $\OO(\kappa^2)$, which implies the inequality \eqref{gA>g1}.
Second, using equations \eqref{op_uplow} and  \eqref{h'(A)2}, we obtain that for $1-\delta \le x \le 1-d^2/\kappa^2$,
$$- h'(x)\ge  [2(1-x)\kappa^2 - xd^2] \cdot p^{-1} \tr\left[\left(x^2[(X^{(2)})^\top X^{(2)}]^{-1} + [(X^{(1)})^\top X^{(1)}]^{-1}\right)^{-1}\right]  \gtrsim p\left(d^2 + |x-1|\kappa^2\right).$$
Then with a similar argument as above, we can get that if $1-2d^2/\kappa^2 - p^{-1/4+c}\le x\le 1-\delta$, then
$$ h(x)-h(1) \gtrsim p\frac{d^4}{\kappa^2} +p^{1/2+2c} \kappa^2, $$
%under equation \eqref{choiceofpara0} \HZ{I don't see which condition we want to use here?},
which again implies that $g(x)>g(1)$, i.e. $x$ cannot be the minimizer of $g$. In sum, we obtain that the minimizer $\hat x$ must satisfy equation \eqref{hatw_add1}.
%Next we prove the following estimate on the optimizer $\hat x$: with high probability,
%%\begin{lemma}
%%For the isotropic model, we have
%\be\label{hatv_add1}
%|\hat v - 1|= \OO\left(\cal E\right), \quad \cal E:=\frac{d^2}{\kappa^2} + \frac{\sigma^2}{p\kappa^2} + p^{-1/2 + \e_0 /2+ 2\e}.
%\ee
%%\end{lemma}
%%\begin{proof}
% In fact, from the proof of Claim \ref{lem_hat_v} above, one can check that if $C\cal E \le |w-1| \le 2C\cal E$ for a large enough constant $C>1$, then $|h'(w)|\gtrsim \sigma^2$. Moreover, under equation \eqref{choiceofpara} we have
%$$h(w) =\OO(\sigma^2),\quad \text{for}\quad   |w-1|\le 2C\cal E.$$
%Thus we obtain that for $|w-1|\ge 2C\cal E$,
%$$\left|h(w) - h(\hat w)\right|\ge |h(w)-\min\{h(w_1),h(w_2)\}|\gtrsim \sigma^2 \cal E \gtrsim \cal E \cdot h(\hat w),$$
%which leads to $g(w) > g(\hat w)$ with high probability by equation \eqref{boundv-w}. Thus $w$ cannot be a minimizer of $g(v)$, and we must have $|\hat v - 1|\le 2C\cal E$. %Together with equation \eqref{hatw_add1}, we conclude equation \eqref{hatv_add1}.
%%\end{proof}
%
%{\cor require $\kappa^2\gg d^2 + p^{-1/2+c}\sigma^2$}
\end{proof}

\paragraph{Part $2$: a reduction to the bias and variance limits.}
Recall that the hard parameter sharing estimator $\hat{\beta}_2^{\MTL}$ is equal to $\hat{B} \hat{A}_2$.
The predication loss of hard parameter sharing is as follows
\begin{align}
L(\hat{\beta}_2^{\MTL}) &=\left\|\Sigma_2^{1/2} \left( \hat B \hat A_2 - \beta^{(2)}\right)\right\| \nonumber\\
&=  \left\| (\Sigma^{(2)})^{1/2}\hat \Sigma(\hat x)^{-1} \left[(X^{(1)})^\top X^{(1)} (\hat x\beta^{(1)}-\hat x^2\beta^{(2)})+ (X^{(2)})^\top \epsilon^{(2)} + \hat x   (X^{(1)})^\top \epsilon^{(1)} \right]\right\|^2.\label{Lbeta_HPS}
\end{align}
Using Lemma \ref{lem_hat_v} and the concentration estimates in Lemma \ref{largedeviation}, we can simplify $L(\hat{\beta}_2^{\MTL})$ as in the following claim.

\begin{claim}\label{claim_reduction}
Recall that $\hat \Sigma(1)$ is equal to $\hat \Sigma$ (cf. Section \ref{sec_diff}).
In the setting of Proposition \ref{cor_MTL_loss}, we have that with high probability
\begin{align*}
&\left|L(\hat{\beta}_2^{\MTL}) - d^2\cdot {p}^{-1}\tr\left[\hat\Sigma^{-2} \left((X^{(1)})^\top X^{(1)} \right)^2\right] -\sigma^2  \bigtr{{\hat \Sigma^{-1}  }}\right| \nonumber\\
\lesssim&  \frac{d^4 + \sigma^2 d^2}{\kappa^2}+p^{-1/2+2c}\kappa^2 +  p^{-1/4+c} (\sigma^2 +d^2).
\end{align*}
\end{claim}
\begin{proof}
Our proof is divided into two steps. First, with the concentration estimates in Lemma \ref{largedeviation}, we can simplify $L(\hat{\beta}_2^{\MTL})$ as follows. With high probability, we have that for any small constant $c>0$,
\be\label{claim_largedev2} \left| L(\hat{\beta}_2^{\MTL})- \cal L(\hat x)\right| \le p^{-1/2+c} \left(\sigma^2 +\kappa^2 +d^2 \right),
\ee
where the function $\cal L(\hat x)$ is defined as
\begin{align*}
	\cal L(\hat x)	:=  &\hat x^2\left[(\hat x-1)^2 \kappa^2 + \frac{(\hat x^2+1)d^2}2\right] \cdot p^{-1}\bigtr{ (X^{(1)})^{\top}X^{(1)} \hat\Sigma(\hat x)^{-1} \Sigma^{(2)} \hat\Sigma(\hat x)^{-1} (X^{(1)})^{\top}X^{(1)} } \\
	& +\sigma^2\cdot \tr\left(\Sigma^{(2)}\hat \Sigma(\hat x)^{-1}\right).
\end{align*}
% \end{claim}
We are ready to finish the proof of Claim \ref{claim_reduction}.
We defer the proof of equation \eqref{claim_largedev2} until the end.
Next, we can further simplify $\cal L(\hat x)$ using Claim \ref{lem_hat_v} and $\Sigma^{(1)}=\Sigma^{(2)}=\id_p$.
More precisely, we claim that with high probability
\begin{align}
&\left|\cal L(\hat x)- d^2\cdot {p}^{-1}\tr\left[\hat\Sigma^{-2} \left((X^{(1)})^\top X^{(1)} \right)^2\right] -\sigma^2  \bigtr{\hat \Sigma^{-1}  }\right| \nonumber\\
&\lesssim  \frac{d^4 + \sigma^2 d^2}{\kappa^2}+p^{-1/2+2c}\kappa^2 +  p^{-1/4+c} (\sigma^2 +d^2). \label{simple12}
\end{align}
Combining \eqref{claim_largedev2} and \eqref{simple12}, we obtain Claim \ref{claim_reduction}.

It remains to prove equation \eqref{simple12}. Using Lemma \ref{lem_hat_v} and equations \eqref{op_X12}-\eqref{op_Sig1}, we obtain that with high probability,
\begin{align}
 \|\hat\Sigma^{-1}-\hat\Sigma(\hat x)^{-1}\| &\le |\hat x^2-1|\|\hat\Sigma^{-1}\| \| (X^{(1)})^\top X^{(1)}\|\|\hat\Sigma(\hat x)^{-1}\|  \lesssim p^{-1}\left(\frac{d^2}{\kappa^2} + p^{-1/4+c}\right).\label{est111}
\end{align}
Using similar arguments, we get that with high probability,
\begin{align}\label{est222}
&\left\|\left(\hat\Sigma^{-2}-\hat\Sigma(\hat x)^{-2}\right)\left((X^{(1)})^\top X^{(1)} \right)^2\right\| \lesssim  \frac{d^2}{\kappa^2} + p^{-1/4+c} .
\end{align}
Moreover, using equations \eqref{op_X12}-\eqref{op_Sig1} we can bound that with high probability,
%$$\bignorm{ (X^{(1)})^{\top}X^{(1)} \hat\Sigma^{-1} \Sigma^{(2)} \hat\Sigma^{-1} (X^{(1)})^{\top}X^{(1)}}\lesssim 1.$$
%which further implies that with high probability,
\begin{align}
& \bigtr{ \hat\Sigma^{-2} \left((X^{(1)})^{\top}X^{(1)}\right)^2}  \le p \bignorm{\hat\Sigma^{-2} \left((X^{(1)})^{\top}X^{(1)}\right)^2}\lesssim p.\label{est333}
\end{align}
Now we bound the left hand side of equation \eqref{simple12} as
\begin{align*}
&\left|\cal L(\hat x)-\frac{d^2}{p}\tr\left[\hat\Sigma^{-2} \left((X^{(1)})^\top X^{(1)} \right)^2\right] -\sigma^2  \tr\left({\hat\Sigma^{-1}  }\right)\right| \\
&\lesssim \left(|\hat x-1|^2 \kappa^2 + |\hat x-1|d^2\right)\cdot p^{-1}\bigtr{ \hat\Sigma^{-2} \left((X^{(1)})^{\top}X^{(1)}\right)^2 } \\
&+ \frac{d^2}{p}\left|\tr\left[\left(\hat\Sigma(\hat x)^{-2}-\hat\Sigma^{-2}\right) \left((X^{(1)})^\top X^{(1)} \right)^2\right]\right|+ \sigma^2  \left|\bigtr{\hat\Sigma(\hat x)^{-1}-\hat\Sigma^{-1}  }\right|.
\end{align*}
Applying the estimates \eqref{hatw_add1}, \eqref{est111}, \eqref{est222} and \eqref{est333} to the three terms on the right-hand side, we can conclude \eqref{simple12}.

Now we give the proof of the estimate \eqref{claim_largedev2}.
The proof of this claim is very similar to Claim \ref{claim_largedev1}, where the only difference is that $\hat x$ now may depend on $\epsilon^{(1)}$, $\epsilon^{(2)}$, $\beta^{(1)}$ and $\beta^{(2)}$.
In this case, we can still use  Lemma \ref{largedeviation} to conclude the proof because $\hat x$ can be pulled out as a coefficient.
Here we only give a proof sketch and omit the details.
Recall that $\beta_0$ is the shared component of $\beta^{(1)}$ and $\beta^{(2)}$ with i.i.d. Gaussian entries of mean zero and variance $p^{-1}\kappa^2$. Moreover, we denote the task-specific components by $\wt\beta^{(1)}$ and $\wt\beta^{(2)}$, whose entries are i.i.d. Gaussian random variables of mean zero and variance $p^{-1} d^2 / 2$. Then we write $L(\hat{\beta}_2^{\MTL}) $ in \eqref{Lbeta_HPS} as:
\begin{align}
L(\hat{\beta}_2^{\MTL})  =&  \left\| (\Sigma^{(2)})^{1/2}\hat \Sigma(\hat x)^{-1} \left[(X^{(1)})^\top X^{(1)} (\hat x -\hat x^2)\beta_0+(X^{(1)})^\top X^{(1)} \hat x\wt \beta^{(1)} - (X^{(1)})^\top X^{(1)}  \hat x^2\wt \beta^{(2)} \right] \right. \nonumber\\
&\left. + (\Sigma^{(2)})^{1/2}\hat \Sigma(\hat x)^{-1}\left[ (X^{(2)})^\top \epsilon^{(2)} + \hat x   (X^{(1)})^\top \epsilon^{(1)} \right]\right\|^2. \label{expand_15}
\end{align}
As in \eqref{expand_6}, we can expand this expression into the sum of 15 terms, and bound each term as in \eqref{eq_hA1}-\eqref{eq_hA56}. For example, for the main term $\hat x^2 (\wt \beta^{(1)})^\top (X^{(1)})^\top X^{(1)} \hat \Sigma(\hat x)^{-1}  \Sigma^{(2)} \hat \Sigma(\hat x)^{-1}  (X^{(1)})^\top X^{(1)}\wt\beta^{(1)}$, using 
Lemma \ref{largedeviation} and equation \eqref{op_X12}-\eqref{op_Sig1}, we can obtain the following estimate with high probability:
\begin{align*}
&  \left| (\wt \beta^{(1)})^\top (X^{(1)})^\top X^{(1)} \hat \Sigma(\hat x)^{-1}  \Sigma^{(2)} \hat \Sigma(\hat x)^{-1}  (X^{(1)})^\top X^{(1)}\wt\beta^{(1)} - \frac{d^2}{2} \cdot p^{-1}\bigtr{(X^{(1)})^\top X^{(1)} \hat \Sigma(\hat x)^{-1}  \Sigma^{(2)} \hat \Sigma(\hat x)^{-1}  (X^{(1)})^\top X^{(1)}}\right| \\
&\le p^{-1+c}d^2 \cdot \left\| (X^{(1)})^\top X^{(1)} \hat \Sigma(\hat x)^{-1}  \Sigma^{(2)} \hat \Sigma(\hat x)^{-1}  (X^{(1)})^\top X^{(1)} \right\|_F \\
&\le p^{-1/2+c}d^2 \cdot  \left\| (X^{(1)})^\top X^{(1)} \hat \Sigma(\hat x)^{-1}  \Sigma^{(2)} \hat \Sigma(\hat x)^{-1}  (X^{(1)})^\top X^{(1)} \right\|  \lesssim p^{-1/2+c}d^2.
\end{align*} 
For the cross term $\hat x (\wt \beta^{(1)})^\top (X^{(1)})^\top X^{(1)} \hat \Sigma(\hat x)^{-1}  \Sigma^{(2)} \hat \Sigma(\hat x)^{-1}  (X^{(2)})^\top  \epsilon^{(2)}$, using Lemma \ref{largedeviation} and \eqref{op_X12}-\eqref{op_Sig1}, we can obtain the following estimate with high probability for any small constant $c>0$:
\begin{align*}
 \left| (\wt \beta^{(1)})^\top (X^{(1)})^\top X^{(1)} \hat \Sigma(\hat x)^{-1}  \Sigma^{(2)} \hat \Sigma(\hat x)^{-1}  (X^{(2)})^\top  \epsilon^{(2)}\right|  & \le p^c \cdot \sigma\sqrt{p^{-1}d^2} \cdot \|(X^{(1)})^\top X^{(1)} \hat \Sigma(\hat x)^{-1}  \Sigma^{(2)} \hat \Sigma(\hat x)^{-1}  (X^{(2)})^\top  \|_F \\
&\lesssim p^{c}\sigma d \cdot  \|(X^{(1)})^\top X^{(1)} \hat \Sigma(\hat x)^{-1}  \Sigma^{(2)} \hat \Sigma(\hat x)^{-1}  (X^{(2)})^\top  \| \\
&\lesssim p^{-1/2+c}\sigma d\le p^{-1/2+c}(\sigma^2+ d^2).
\end{align*}
The rest of the terms in the expansion of \eqref{expand_15} can be bounded in the same way, and we omit the details.
 \end{proof}

>>>>

h(x):= [(1-x^{-1})^2\kappa^2 + (1+x^{-2})d^2] \cdot p^{-1} \tr\left[\left([(X^{(2)})^\top X^{(2)}]^{-1} + x^{-2} [(X^{(1)})^\top X^{(1)}]^{-1}\right)^{-1}\right].

@@

h'(x) \ge \left[2(1-x^{-1})\frac{\kappa^2}{x^2} - 2\frac{d^2}{x^3}\right] \cdot p^{-1} \tr\left[\left([(X^{(2)})^\top X^{(2)}]^{-1} + x^{-2} [(X^{(1)})^\top X^{(1)}]^{-1}\right)^{-1}\right] \ge 0,

@@

as long as $x \ge 1+d^2/\kappa^2$.

@@

	h'(x)\le [-2(1-x)\kappa^2 +2 xd^2] \cdot p^{-1} \tr\left[\left(x^2[(X^{(2)})^\top X^{(2)}]^{-1} + [(X^{(1)})^\top X^{(1)}]^{-1}\right)^{-1}\right]\le 0,

@@

as long as $x\le 1-d^2/\kappa^2$. In sum, we see that the minimizer $x^\star$ must satisfy
$$1-d^2/\kappa^2\le x^\star \le 1+d^2/\kappa^2.$$

@@

Now we are ready to prove equation \eqref{hatw_add1}. First, using equations \eqref{op_uplow} and  \eqref{h'(A)1}, we obtain that for $1+3d^2/(2\kappa^2) \le x\le 1+\delta$,
$$h'(x)\ge \frac{2(x-1)\kappa^2 - 2d^2}{x^3} \cdot p^{-1} \tr\left[\left([(X^{(2)})^\top X^{(2)}]^{-1} + x^{-2} [(X^{(1)})^\top X^{(1)}]^{-1}\right)^{-1}\right] \gtrsim p\left(d^2 + |x-1|\kappa^2\right).$$
Thus we get that if $1+2d^2/\kappa^2 +p^{-1/4+c}\le x\le 1+\delta$,
\begin{align*}
h(x)-h(1)\ge h(x)-h\left(1+\frac{3d^2}{2\kappa^2}\right) \ge \int_{1+\frac{3d^2}{2\kappa^2}}^x h'(x)\dd x \gtrsim p\kappa^2 \cdot |x-1|^2  \gtrsim p\frac{d^4}{\kappa^2} + p^{1/2+2c} \kappa^2 .
\end{align*}
On the other hand, by Claim \ref{claim_largedev1} we have that
$$ g(x)=h(x)+\sigma^2 (n_1+n_2-p)+\OO \left(p^{1/2+c}\left(\sigma^2 +\kappa^2+d^2 \right)\right)$$
with high probability. Combining the above two estimates, we obtain that under the conditions $\sigma^2 =\OO( \kappa^2)$ and $d^2 =\oo({\kappa^2})$,
$$g(x)-g(1) = h(x)-h(1) + \OO \left(p^{1/2+c}\left(\sigma^2 +\kappa^2+d^2 \right)\right) >0$$
with high probability, i.e. $x$ cannot be the minimizer of $g$.
%Then if we choose the constant $c$ in Claim \ref{claim_largedev1} such that $e_1<2e_2$, we have
%$$ h(x)-h(1)\gtrsim  p^{-1/2+2e_2}\cdot p\kappa^2 \gg p^{-1/2+e_1}\cdot p\left(\sigma^2 +\kappa^2+d^2 \right),$$ where we use the assumption that $\sigma^2$ and $d^2$ are both at most $\OO(\kappa^2)$, which implies the inequality \eqref{gA>g1}.
Second, using equations \eqref{op_uplow} and  \eqref{h'(A)2}, we obtain that for $1-\delta \le x \le 1-3d^2/(2\kappa^2)$,
$$- h'(x)\ge  [2(1-x)\kappa^2 - 2xd^2] \cdot p^{-1} \tr\left[\left(x^2[(X^{(2)})^\top X^{(2)}]^{-1} + [(X^{(1)})^\top X^{(1)}]^{-1}\right)^{-1}\right]  \gtrsim p\left(d^2 + |x-1|\kappa^2\right).$$
Then with a similar argument as above, we can get that if $1-2d^2/\kappa^2 - p^{-1/4+c}\le x\le 1-\delta$, then
$$ h(x)-h(1) \gtrsim p\frac{d^4}{\kappa^2} +p^{1/2+2c} \kappa^2, $$
%under equation \eqref{choiceofpara0} \HZ{I don't see which condition we want to use here?},
which again implies that $g(x)>g(1)$, i.e. $x$ cannot be the minimizer of $g$. In sum, we obtain that the minimizer $\hat x$ of $g$ must satisfy equation \eqref{hatw_add1}.
%Next we prove the following estimate on the optimizer $\hat x$: with high probability,
%%\begin{lemma}
%%For the isotropic model, we have
%\be\label{hatv_add1}
%|\hat v - 1|= \OO\left(\cal E\right), \quad \cal E:=\frac{d^2}{\kappa^2} + \frac{\sigma^2}{p\kappa^2} + p^{-1/2 + \e_0 /2+ 2\e}.
%\ee
%%\end{lemma}
%%\begin{proof}
% In fact, from the proof of Claim \ref{lem_hat_v} above, one can check that if $C\cal E \le |w-1| \le 2C\cal E$ for a large enough constant $C>1$, then $|h'(w)|\gtrsim \sigma^2$. Moreover, under equation \eqref{choiceofpara} we have
%$$h(w) =\OO(\sigma^2),\quad \text{for}\quad   |w-1|\le 2C\cal E.$$
%Thus we obtain that for $|w-1|\ge 2C\cal E$,
%$$\left|h(w) - h(\hat w)\right|\ge |h(w)-\min\{h(w_1),h(w_2)\}|\gtrsim \sigma^2 \cal E \gtrsim \cal E \cdot h(\hat w),$$
%which leads to $g(w) > g(\hat w)$ with high probability by equation \eqref{boundv-w}. Thus $w$ cannot be a minimizer of $g(v)$, and we must have $|\hat v - 1|\le 2C\cal E$. %Together with equation \eqref{hatw_add1}, we conclude equation \eqref{hatv_add1}.
%%\end{proof}
%
%{\cor require $\kappa^2\gg d^2 + p^{-1/2+c}\sigma^2$}
\end{proof}

\paragraph{Part $2$: a reduction to the bias and variance limits.}
Recall that the hard parameter sharing estimator $\hat{\beta}_2^{\MTL}$ is equal to $\hat{B} \hat{A}_2$.
The predication loss of hard parameter sharing is as follows
\begin{align}
L(\hat{\beta}_2^{\MTL}) &=\left\|(\Sigma^{(2)})^{1/2} \left( \hat B \hat A_2 - \beta^{(2)}\right)\right\| \nonumber\\
&=  \left\| (\Sigma^{(2)})^{1/2}\hat \Sigma(\hat x)^{-1} \left[(X^{(1)})^\top X^{(1)} (\hat x\beta^{(1)}-\hat x^2\beta^{(2)})+ (X^{(2)})^\top \epsilon^{(2)} + \hat x   (X^{(1)})^\top \epsilon^{(1)} \right]\right\|^2.\label{Lbeta_HPS}
\end{align}
Using Lemma \ref{lem_hat_v} and the concentration estimates in Lemma \ref{largedeviation}, we can simplify $L(\hat{\beta}_2^{\MTL})$ as follows.

\begin{claim}\label{claim_reduction}
Recall that $\hat \Sigma(1)$ is equal to $\hat \Sigma$ (cf. equation \eqref{def hatsig}).
In the setting of Proposition \ref{cor_MTL_loss}, we have the following estimate with high probability for any small constant $c>0$:
\begin{align*}
&\left|L(\hat{\beta}_2^{\MTL}) - \frac{2d^2}{p}\tr\left[\hat\Sigma^{-2} \left((X^{(1)})^\top X^{(1)} \right)^2\right] -\sigma^2  \tr\left({\hat \Sigma^{-1}  }\right)\right| \nonumber\\
\lesssim&  \frac{d^4 + \sigma^2 d^2}{\kappa^2}+p^{-1/2+2c}\kappa^2 +  p^{-1/4+c} (\sigma^2 +d^2).
\end{align*}
\end{claim}
\begin{proof}
Our proof is divided into two steps. First, with the concentration estimates in Lemma \ref{largedeviation}, we can simplify $L(\hat{\beta}_2^{\MTL})$ as follows. With high probability, we have that for any small constant $c>0$,
\be\label{claim_largedev2} \left| L(\hat{\beta}_2^{\MTL})- \cal L(\hat x)\right| \le p^{-1/2+c} \left(\sigma^2 +\kappa^2 +d^2 \right),
\ee
where the function $\cal L(\hat x)$ is defined as
\begin{align*}
	\cal L(\hat x)	:=  &\hat x^2\left[(\hat x-1)^2 \kappa^2 +  (\hat x^2+1)d^2 \right] \cdot p^{-1}\bigtr{ (X^{(1)})^{\top}X^{(1)} \hat\Sigma(\hat x)^{-1} \Sigma^{(2)} \hat\Sigma(\hat x)^{-1} (X^{(1)})^{\top}X^{(1)} } \\
	& +\sigma^2\cdot \tr\left(\Sigma^{(2)}\hat \Sigma(\hat x)^{-1}\right).
\end{align*}
% \end{claim}
%We are now ready to finish the proof of Claim \ref{claim_reduction}.
We defer the proof of equation \eqref{claim_largedev2} until the end.
Next, we can further simplify $\cal L(\hat x)$ using Claim \ref{lem_hat_v} and $\Sigma^{(1)}=\Sigma^{(2)}=\id_{p\times p}$.
More precisely, we claim that with high probability
\begin{align}
&\left|\cal L(\hat x)- \frac{2d^2}{p} \tr\left[\hat\Sigma^{-2} \left((X^{(1)})^\top X^{(1)} \right)^2\right] -\sigma^2  \tr\left(\hat \Sigma^{-1}  \right)\right| \nonumber\\
\lesssim & \frac{d^4 + \sigma^2 d^2}{\kappa^2}+p^{-1/2+2c}\kappa^2 +  p^{-1/4+c} (\sigma^2 +d^2). \label{simple12}
\end{align}
Combining equations \eqref{claim_largedev2} and \eqref{simple12}, we conclude Claim \ref{claim_reduction}.

Now we prove equation \eqref{simple12}. Using Claim \ref{lem_hat_v} and equations \eqref{op_X12} and \eqref{op_Sig1}, we obtain that with high probability,
\begin{align}
 \|\hat\Sigma^{-1}-\hat\Sigma(\hat x)^{-1}\| &\le |\hat x^2-1|\|\hat\Sigma^{-1}\| \| (X^{(1)})^\top X^{(1)}\|\|\hat\Sigma(\hat x)^{-1}\|  \lesssim p^{-1}\left(\frac{d^2}{\kappa^2} + p^{-1/4+c}\right).\label{est111}
\end{align}
Using similar arguments, we get that with high probability,
\begin{align}\label{est222}
&\left\|\left(\hat\Sigma^{-2}-\hat\Sigma(\hat x)^{-2}\right)\left((X^{(1)})^\top X^{(1)} \right)^2\right\| \lesssim  \frac{d^2}{\kappa^2} + p^{-1/4+c} .
\end{align}
Moreover, using equations \eqref{op_X12} and \eqref{op_Sig1}, we can bound that with high probability,
%$$\bignorm{ (X^{(1)})^{\top}X^{(1)} \hat\Sigma^{-1} \Sigma^{(2)} \hat\Sigma^{-1} (X^{(1)})^{\top}X^{(1)}}\lesssim 1.$$
%which further implies that with high probability,
\begin{align}
& \bigtr{ \hat\Sigma^{-2} \left((X^{(1)})^{\top}X^{(1)}\right)^2}  \le p \bignorm{\hat\Sigma^{-2} \left((X^{(1)})^{\top}X^{(1)}\right)^2}\lesssim p.\label{est333}
\end{align}
We can bound the left hand side of equation \eqref{simple12} as
\begin{align*}
&\left|\cal L(\hat x)-\frac{2d^2}{p}\tr\left[\hat\Sigma^{-2} \left((X^{(1)})^\top X^{(1)} \right)^2\right] -\sigma^2  \tr\left({\hat\Sigma^{-1}  }\right)\right| \\
\lesssim &\left(|\hat x-1|^2 \kappa^2 + |\hat x-1|d^2\right)\cdot p^{-1}\bigtr{ \hat\Sigma^{-2} \left((X^{(1)})^{\top}X^{(1)}\right)^2 } \\
&+ \frac{d^2}{p}\left|\tr\left[\left(\hat\Sigma(\hat x)^{-2}-\hat\Sigma^{-2}\right) \left((X^{(1)})^\top X^{(1)} \right)^2\right]\right|+ \sigma^2  \left|\bigtr{\hat\Sigma(\hat x)^{-1}-\hat\Sigma^{-1}  }\right|.
\end{align*}
Applying the estimates \eqref{hatw_add1}, \eqref{est111}, \eqref{est222} and \eqref{est333} to the three terms on the right-hand side, we can conclude \eqref{simple12}.

Finally we give the proof of the estimate \eqref{claim_largedev2}.
The proof of this claim is very similar to Claim \ref{claim_largedev1}, where the only difference is that $\hat x$ now may depend on $\epsilon^{(1)}$, $\epsilon^{(2)}$, $\beta^{(1)}$ and $\beta^{(2)}$.
In this case, we can still use  Lemma \ref{largedeviation} to conclude the proof because $\hat x$ can be pulled out as a coefficient.
Here we only give a proof sketch and omit the details.
Recall that $\beta_0$ is the shared component of $\beta^{(1)}$ and $\beta^{(2)}$ with i.i.d. Gaussian entries of mean zero and variance $p^{-1}\kappa^2$. Moreover, we denote the task-specific components by $\wt\beta^{(1)}$ and $\wt\beta^{(2)}$, whose entries are i.i.d. Gaussian random variables of mean zero and variance $p^{-1} d^2 $. Then we write $L(\hat{\beta}_2^{\MTL}) $ in \eqref{Lbeta_HPS} as:
\begin{align}
L(\hat{\beta}_2^{\MTL})  =&  \left\| (\Sigma^{(2)})^{1/2}\hat \Sigma(\hat x)^{-1} \left[(X^{(1)})^\top X^{(1)} (\hat x -\hat x^2)\beta_0+(X^{(1)})^\top X^{(1)} \hat x\wt \beta^{(1)} - (X^{(1)})^\top X^{(1)}  \hat x^2\wt \beta^{(2)} \right] \right. \nonumber\\
&\left. + (\Sigma^{(2)})^{1/2}\hat \Sigma(\hat x)^{-1}\left[ (X^{(2)})^\top \epsilon^{(2)} + \hat x   (X^{(1)})^\top \epsilon^{(1)} \right]\right\|^2. \label{expand_15}
\end{align}
As in equation \eqref{expand_6}, we can expand this expression into the sum of 15 terms, and bound each term as in equations \eqref{eq_hA1}-\eqref{eq_hA56}. For example, for the main term $\hat x^2 (\wt \beta^{(1)})^\top (X^{(1)})^\top X^{(1)} \hat \Sigma(\hat x)^{-1}  \Sigma^{(2)} \hat \Sigma(\hat x)^{-1}  (X^{(1)})^\top X^{(1)}\wt\beta^{(1)}$, using 
Lemma \ref{largedeviation} and equations \eqref{op_X12} and \eqref{op_Sig1}, we can obtain the following estimate with high probability:
\begin{align*}
&  \left| (\wt \beta^{(1)})^\top (X^{(1)})^\top X^{(1)} \hat \Sigma(\hat x)^{-1}  \Sigma^{(2)} \hat \Sigma(\hat x)^{-1}  (X^{(1)})^\top X^{(1)}\wt\beta^{(1)} - \frac{d^2}{p}\bigtr{(X^{(1)})^\top X^{(1)} \hat \Sigma(\hat x)^{-1}  \Sigma^{(2)} \hat \Sigma(\hat x)^{-1}  (X^{(1)})^\top X^{(1)}}\right| \\
&\le p^{-1+c}d^2 \cdot \left\| (X^{(1)})^\top X^{(1)} \hat \Sigma(\hat x)^{-1}  \Sigma^{(2)} \hat \Sigma(\hat x)^{-1}  (X^{(1)})^\top X^{(1)} \right\|_F \\
&\le p^{-1/2+c}d^2 \cdot  \left\| (X^{(1)})^\top X^{(1)} \hat \Sigma(\hat x)^{-1}  \Sigma^{(2)} \hat \Sigma(\hat x)^{-1}  (X^{(1)})^\top X^{(1)} \right\|  \lesssim p^{-1/2+c}d^2.
\end{align*} 
For the cross term $\hat x (\wt \beta^{(1)})^\top (X^{(1)})^\top X^{(1)} \hat \Sigma(\hat x)^{-1}  \Sigma^{(2)} \hat \Sigma(\hat x)^{-1}  (X^{(2)})^\top  \epsilon^{(2)}$, using Lemma \ref{largedeviation} and equations \eqref{op_X12} and \eqref{op_Sig1}, we can obtain the following estimate with high probability for any small constant $c>0$:
\begin{align*}
 \left| (\wt \beta^{(1)})^\top (X^{(1)})^\top X^{(1)} \hat \Sigma(\hat x)^{-1}  \Sigma^{(2)} \hat \Sigma(\hat x)^{-1}  (X^{(2)})^\top  \epsilon^{(2)}\right|  & \le p^c \cdot \sigma\sqrt{p^{-1}d^2} \cdot \|(X^{(1)})^\top X^{(1)} \hat \Sigma(\hat x)^{-1}  \Sigma^{(2)} \hat \Sigma(\hat x)^{-1}  (X^{(2)})^\top  \|_F \\
&\lesssim p^{c}\cdot \sigma d \cdot  \|(X^{(1)})^\top X^{(1)} \hat \Sigma(\hat x)^{-1}  \Sigma^{(2)} \hat \Sigma(\hat x)^{-1}  (X^{(2)})^\top  \| \\
&\lesssim p^{-1/2+c}\sigma d\le p^{-1/2+c}(\sigma^2+ d^2).
\end{align*}
The rest of the terms in the expansion of \eqref{expand_15} can be bounded in the same way, and we omit the details.
 \end{proof}
